### 2023-07-04 paper/sec-summary.tex
Update sec-summary.tex

Several avenues extending the results of this work may be foreseen.
%
First of all, as the design of the proposed FPF experiments
becomes more advanced and concrete, it should be possible more reliable
estimate of corrections, may become the limiting factor
for this kind of analyses.
%
Improve event generation, based on {\sc\small Pythia}
modern QCD generator with higher order QCD corrections,
why improve estimates better modelling of final state acceptance.
%
Analysis also SIS region low $Q$, improve modelling of low-$Q$ cross-sections
relevant for atmospheric and oscillation neutrino experiments.
%
Neglect flux uncertainties, joint determination

All in all, Our analysis highlights how exploiting the potential
 of this unique neutrino beam  effectively
extends the LHC with a ``Neutrino-Ion Collider''.

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement.

>>>>

Several avenues extending the results of this work may be foreseen.
%
First of all, as the design of the proposed FPF experiments
becomes more advanced and concrete, it should be possible
to construct more accurate estimates of the systematic
uncertainties and of their bin-by-bin correlations,
which may eventually become the limiting factor
for hadron structure analyses with LHC neutrinos.
%
Second, scattering analyses with LHC neutrinos would benefit from
the use of Monte Carlo event generators accounting
for higher-order QCD corrections.
%
As compared to the currently used LO generators,
these would improve the modelling of the final-state leptonic
and hadronic kinematics, which in turn determine the acceptance rate
of the reconstructed events.
%
Further, the predictions from such precise Monte Carlo generators
should eventually be folded with a full-fledged detector simulation
in order to robust determine selection efficiencies, e.g.
such as those related to charm tagging.

Third, while in this work we have focused on the deep-inelastic
region, ongoing and future LHC experiments also provide
important information on the shallow-inelastic scattering (SIS)
region at low values of $Q$~\cite{Candido:2023utz}, relevant for inclusive cross-sections
entering atmospheric and oscillation neutrino experiments.
%
By means of a similar approach, it should be possible to quantify
the improvements that LHC neutrino data can provide on models
of neutrino scattering in the poorly-understood SIS region.
%
Finally, in this work we have taken the incoming muon neutrino flux
as a given and neglected any associated uncertainties.
%
However, ultimately one may need to constrain at the same time
the incoming fluxes and the neutrino scattering cross-sections
from the recorded event rates.
%
Such joint interpretation would require extending the present
analysis with additional theory nuisance parameters modelling
deviations of the neutrino flux with respect to the baseline predictions.

All in all, our findings highlight how exploiting
the LHC neutrino beam for hadron structure studies effectively
extends the LHC with a ``Neutrino-Ion Collider'', a charged
current-counterpart of the EIC, and that we are still
scratching the surface of the uncharted
scientific potential of such experiments.

\subsection*{Acknowledgments}
%
We are grateful to many colleagues involved in the Forward
Physics Facility initiative for many illuminating
discussions and encouragement.
%
We thank Akitaka Ariga and Tomoko Ariga for information
concerning FASER$\nu$2,
Wenjie Wu and Steven Linden concerning FLArE,
and Antonia di Crescenzo concerning AdvSND.
